### 2013-09-22 manuscripts/reply/reply.tex
Initial draft of reply complete.
Sending this version to co-authors.

        \vspace{12pt}
        Jamie R. Oaks$^{1,2,5}$, Jeet Sukumaran$^{1,2}$, Jacob A.
        Esselstyn$^{3}$, Charles W. Linkem$^{1,2}$, Cameron D.
        Siler$^{4}$, Mark T. Holder$^{2}$ and Rafe M. Brown$^{1,2}$

        \bigskip
        $^1$\emph{Biodiversity Institute\\
            $^2$Department of Ecology and Evolutionary Biology\\ 
            University of Kansas\\
            %1345 Jayhawk Blvd\\
            Lawrence, KS 66045\\
            USA}\\[.1in]
        $^3$\emph{Biology Department\\
            McMaster University\\
            % Life Sciences Building Rm 328\\
            Hamilton, Ontario L8S4K1\\
            Canada}\\[.1in]
        $^4$\emph{Department of Biology\\
            University of South Dakota\\
            Vermillion, SD 57069\\
            USA}\\[.1in]
        $^5$\emph{Corresponding author} (\href{mailto:joaks1@ku.edu}{\tt
        joaks1@ku.edu})\\

@@

{\sffamily
    \noindent\textbf{ABSTRACT} \\
    \noindent Abstract here \ldots

    \vspace{12pt}
    \noindent\textbf{KEY WORDS: } 
}

\newpage
\noindent Recently, this journal has served as a venue for discussion of the
potential pitfalls of approximate Bayesian methods of comparative
phylogeographical model choice.
The discussion is centered around the approximate Bayesian model choice method,
\msb, which estimates the temporal distribution of divergences among
co-distributed pairs of taxa \citep{Huang2011}.
\citet{Oaks2012} published their findings that the method \msb can often be
biased towards inferring models of temporally clustered divergence times among
taxon pairs.
\citet{Hickerson2013} has published a response to this paper where they
present a model-averaging approach that they conclude circumvents the poor
behavior of the method revealed by \citet{Oaks2012}.
Both of these papers are largely in agreement.
In fact, \citet{Hickerson2013} reiterate a lot of the discussion of
\citet{Oaks2012} regarding the impact of broad uniform priors on Bayesian model
choice.
The main differences in their perspectives are centered around
(1) the mechanism by which broad uniform priors cause the poor behavior of
\msb, and
(2) how to potentially ameliorate this issue.

Regarding the mechanism behind the poor behavior of the method,
\citet{Oaks2012} suggest the primary cause is likely the low marginal
likelihoods of parameter-rich models integrated over vast parameter space with
low probability of producing the data, yet relatively high prior density
\citep[this is often referred to as Lindley's paradox;][]{Lindley1957}.
Note, this suggests the bias is extrinsic to \msb, and the numerical
approximation machinery of the method could be sound.
\citet{Hickerson2013} take a more pessimistic view of the bias, and suggest it
is intrinsic to \msb.
They conclude the method's rejection algorithm is inefficient and will be
increasingly biased as the overall space of the model increases, either as a
function of the number of taxon pairs or the width of the uniform priors on
nuisance parameters.
They support their position by giving a probabilistic argument that focuses on
only one of the three prior models used by \citet{Oaks2012}.
We show that this argument is based on dubious assumptions, and does not
explain the bias of the method found in several analyses of \citet{Oaks2012}.
Furthermore, we reiterate several of the findings of \citet{Oaks2012} as well
as present results of additional analyses, which strongly suggest that
Lindley's paradox is playing a large role in the poor behavior of the method.

As for how to mitigate the bias, \citet{Oaks2012} suggest that more cogent
prior probability distributions on divergence models and nuisance parameters
could reduce the effect of Lindley's paradox.
They also layout a set of simulation-based procedures for determining power,
accuracy, and robustness of the method given a dataset, and recommend any
application of \msb should be accompanied by such procedures, especially
if any biological conclusions are going to drawn from the results.
\citet{Hickerson2013} present an approximate Bayesian model-averaging approach
for accommodating uncertainty in selecting among empirically guided priors, and
champion the method as a means of avoiding the pitfalls raised by
\citet{Oaks2012}.
Unfortunately, we show that fundamental errors in this approach render some of
their results invalid and leave the remaining results difficult to interpret.
Furthermore, we follow the advice of \citet{Oaks2012} and present
simulation-based assessments of Hickerson et al.'s \citeyear{Hickerson2013}
approach.
Our results demonstrate that the method is biased and dangerous.  The approach
merely provides another means by which the model can ``escape'' large parameter
space, and bias towards smaller models remains.
This manifestation of the bias can be dangerous and often excludes the true
parameter space due to the use of uniform priors.
Furthermore we discuss the potential theoretical and practical problems of
empirical Bayesian model choice, which is encouraged by \citet{Hickerson2013}
without any mention of its potential complications.

\section*{Hickerson et al.'s re-analysis of the Philippines data}
\citet{Hickerson2013} re-analyze the dataset of \citet{Oaks2012} using a
model-averaging approach, where they place a discrete uniform prior over eight
different prior models (see Table 1 of \citet{Hickerson2013}).
In our initial attempts to explore the behavior of this approach, we found
a fundamental error in the methodology of \citet{Hickerson2013}:
their model mixes different time units.

Each of the eight prior models used in the re-analysis by \citet{Hickerson2013}
has one of two priors on the mean population size of the descendant populations
of each taxon pair:
$\meanDescendantTheta{} \sim U(0.0001, 0.1)$ or
$\meanDescendantTheta{} \sim U(0.0005, 0.04)$ or
As described in \citet{Oaks2012}, the divergence time parameters of the model
implemented in \msb are scaled relative to a constant reference population
size, \myTheta{C}.
This reference population size is defined in terms of the upper limit on the
uniform prior on the mean population size of the descendant populations,
\meanDescendantTheta{}, such that for the prior $\meanDescendantTheta{} \sim
U(\uniformMin{\meanDescendantTheta{}},\uniformMax{\meanDescendantTheta{}})$,
$\myTheta{C} = \uniformMax{\meanDescendantTheta{}}/2$.
Thus, the model used by \citet{Hickerson2013} mixes two different units of
time.
In other words, some of their prior and posterior samples are in units of
$0.05/\mutationRate$ generations, whereas others are in units of
$0.02/\mutationRate$ generations.

The fact that their posterior samples are in different units makes the results
of \citet{Hickerson2013} difficult to interpret, and renders their
regression-adjusted results invalid; a fundamental assumption of regression is
that all of the values of the response variable are in the same units.
Thus, the results in sections ``Using ABC Model Comparison to Weight
Alternative Priors for the Philippine Vertebrate Data'' and ``Improved Sampling
Efficiency by Prior Weighting Supports Asynchronous and Recent Divergence for
the Philippines Vertebrate Data'' and presented in Figure 2 of
\citet{Hickerson2013} should be disregarded.
The error is easily illustrated by re-plotting their results with the different
time units indicated (Figure~\ref{figJointPosteriorHickerson}.

@@

\section*{The dangers of empirical Bayesian model choice}
\citet{Hickerson2013} repeatedly refer to the prior distributions used by
\citet{Oaks2012} as ``poorly selected''.
However, this is bit misleading, as \citet{Oaks2012} discuss in detail how they
selected their priors (see their section ``Specifying and simulating the joint
prior'').
They detail how being limited to uniform prior distributions in \msb
necessitates awkward broad priors to avoid excluding the truth, a priori.
What \citet{Hickerson2013} really mean by ``poorly selected'' is that
\citet{Oaks2012} did not use their data to inform their initial prior
distributions (i.e., they did not use an empirical Bayesian approach).
\citet{Oaks2012} did use empirically informed priors when assessing
both the prior sensitivity of the method and determining the power of \msb
under real-world conditions with highly informative priors.
\citet{Oaks2012} discuss the potential dangers of taking an empirical Bayesian
approach to model choice (see last paragraph of ``Assessing prior sensitivity
of \msb''), and we expand on this here by exploring both the theoretical and
practical implications of using empirically informed priors for Bayesian
model choice.

@@

This is not to say that empirical Bayesian approaches not useful.
Quite the contrary.
Empirical Bayes is a well studied branch of Bayesian statistics that
has given rise to a many powerful inference methods.
It is true that empirical Bayes methods have an uncertain theoretical basis and
do not yield a valid posterior distribution from Bayes' rule \citep[e.g.,
empirical Bayesian estimates of the posterior are often too narrow, off-center,
and misshapen;][]{Morris1983,Laird1987,Carlin1990,Efron2013}.
Nevertheless, empirical Bayes methods can provide a powerful means of parameter
estimation.
Furthermore, many post-hoc correction methods have been developed for
estimating confidence-intervals from empirical Bayes estimates of posterior
distributions that often exhibit good frequentist properties
\citep{Morris1983,Laird1987,Laird1989, Carlin1990,Hwang2009}.

Whereas empirical Bayes approaches can provide powerful methods for parameter
estimation, a theoretical justification for empirical Bayes approaches to model
choice is much more uncertain.
In Bayesian model choice, the goal is not to estimate parameters, but to
estimate the relative probabilities of candidate models.
Unlike parameter estimates, posterior probabilities represent a summary of the
entire posterior distribution.
Thus, given that empirical Bayesian posterior distributions are not accurate,
there is no guarantee regarding the accuracy of probabilities summarized from
them.

This can be demonstrated with a simple, albeit contrived, example.
Let us say that principal investigator Mary and her new postdoc Will are
interested in the hypothesis that the mass of George Washington's periwig
renders the quarter dollar of the United States unfair.
That is to say that their null hypothesis is that the probability of a US
quarter landing heads when tossed is less than 0.5 ($\theta < 0.5$).
They can certainly evaluate this hypothesis, they can have undergraduate
worker, Joe, flip the coin for them while the tabulate the results.
But being Bayesians, before they call Joe into the lab, they agree on a
prior probability to place on the set of all possible probabilities that
the quarter will land heads when it is flipped.
Given their prior knowledge that Joe moonlights as a magician, and is notorious
for performing coin and card tricks in the lab, they suspect there is a good
chance that Joe will use his slight-of-hand skills to replace their quarter
with one of his two-headed or two-tailed coins he has up his sleeve at all
times.
So, knowing that the beta distribution is the conjugate prior for a binomial
likelihood, they decide to use a $beta(a=0.5, b=0.5)$ prior distribution
(Figure~\ref{figCoinFlip}).

Mary calls Joe into the lab, and hands him a regular-issue US quarter minted in
1992.
After five tosses, four of which was heads, Joe decides that academics are
crazy and leaves the lab to pursue a major in theatre.  Mary and Will, both
being computational biologists, are satisfied with their
empirical dataset of $y = 4$ heads out of $N = 5$ trials.
They know from the conjugacy of the beta prior, that the posterior distribution
has the nice analytical form $\theta|y,N \sim beta(a + y, b + N - y)$, which
in this case is simply $beta(4.5, 1.5)$; this is the true posterior distribution
of $\theta$ given their prior belief and data (Figure~\ref{figCoinFlip}).
This allows them to plug these values into the beta cumulative distribution
function to determine that the posterior probability of their hypothesis is
$p(\theta < 0.5 | y=1, N=5) = 0.088$.
Given their prior belief and dataset, this indeed is the correct posterior
probability of the hypothesis, and Mary and Will should now update their
posterior belief accordingly.

However, upon reflecting on the results of their experiment
(Figure~\ref{figCoinFlip}), Mary and Will regret not trusting Joe to refrain
from turning their experiment into a magic trick.
Their prior looks very ``poorly selected,'' and if they had only
had more faith in Joe's integrity, they would have selected a much better
prior. Clearly form their results, they should have used a prior centered
around 0.2; their data suggest a prior of $beta(4.5, 1.5)$ would have been
much more appropriate.
Rather than resort to flipping the coin five more times, Mary and Will decide
to redo their analysis using the much better ``prior'' of $p(\theta) \sim
beta(4.5, 1.5)$.
This gives a ``posterior'' of $\theta|y,N \sim beta(8.5, 2.5)$, and a
probability of their hypothesis of $p(\theta < 0.5 | y=1, N=5) = 0.026$.
Now convinced that the mass of President Washington's head renders the US
Quarter unfair, Will begins composing an e-mail of complaint for the U.S.\
Mint.

If Joe's flips were a representative sample, Mary and Will's empirical Bayes
estimate might very well be a better point estimate for the parameter
\myTheta{}.
However, their empirical Bayes estimate of the probability of their hypothesis
is incorrect and biased.
This simple example shows how parameter estimation is fundamentally different
from estimating the probability of a model.
While empirical informed priors can be used to obtain well-behaved parameter
estimators, using them for model choice is much less certain.

\subsection*{Practical dangers of narrow uniform priors for Bayesian model
choice}
We were alarmed when we saw the results of the model-averaging results
presented in \citet{Hickerson2013}.
Their results strongly favored the models with the narrowest, empirically
informed prior on divergence time, and thus their model-averaged posterior
estimates are dominated by models $M_1$ and $M_2$ (see Table 1 of
\citet{Hickerson2013}).
This concerned us because the narrowest prior of \citet{Hickerson2013}
($\divt{} \sim U(0,0.1)$) likely excludes the true divergence times for at
least some of the Philippine taxa.
They set this prior to match the 95\% highest posterior density (HPD) interval for
the mean divergence time estimated under one of the priors used by
\citet{Oaks2012} (see Table 2 and 3 of \citet{Oaks2012}).
Given this interval estimate is for the \emph{mean} divergence time across all
22 taxa, it seems odd to set this as the prior, because many of the taxon pairs
are expected to have diverged at times older than the upper limit.
Furthermore, this prior is \emph{excluded} from the 95\% HPD interval estimates
of the mean divergence time under the other two priors explored by
\citet{Oaks2012} (under these priors the 95\% HPD is approximately 0.3--0.6;
see Table~6 of \citet{Oaks2012}).
Thus, when we saw the results of \citet{Hickerson2013} we suspected that
Lindley's paradox was again biasing the method toward models with smaller
parameter space, and as a consequence was biasing the method toward models
that exclude the truth (i.e., the model-averaged posterior will
be dominated by models that exclude the true values of parameters of the model).

@@

For our re-analysis of the Philippines dataset we used the model-averaging
approach of \citet{Hickerson2013}, but with different prior models to avoid
their error of mixing time units.
We used five priors, all of which had priors on population sizes of
$\meanDescendantTheta{} \sim U(0.0001, 0.1)$ and $\ancestralTheta{} \sim
U(0.0001, 0.05)$.
Following \citet{Hickerson2013}, each of these priors had the following
priors on divergence time parameters:
$M_1$, $\divt{} \sim U(0, 0.1)$;
$M_2$, $\divt{} \sim U(0, 1)$;
$M_3$, $\divt{} \sim U(0, 5)$;
$M_4$, $\divt{} \sim U(0, 10)$; and
$M_5$, $\divt{} \sim U(0, 20)$.
For our prior, we simulated $1\e6$ random samples from each of the models
for a total sample of $5\e6$.
For each model, we retained the 10,000 samples with the smallest Euclidean
distance from the observed summary statistics, standardizing the statistics
using the prior means and standard deviations of the given model.
From the remaining 50,000 samples, we then retained the 10,000 samples with the
smallest Euclidean distance from the observed summary statistics, this time
standardizing the statistics using the prior means and standard deviations
across all five models.
We then repeated this analysis twice, replacing the $M_1$ with
$M_1A$ and $M_1B$, which differ only by having priors on divergence
times of $\divt{} \sim U(0, 0.01)$ and $\divt{} \sim U(0, 0.001)$,
respectively.
While we suspect the prior of $\divt{} \sim U(0, 0.1)$ used by
\citet{Hickerson2013} likely excludes the true divergence times of at least
some of the 22 taxa, we are nearly certain that these narrower priors are
incorrect and exclude most, if not all, of the divergence times of the
Philippine taxa.

Our results show that the model-averaging approach of \citet{Hickerson2013}
does not reduce the methods bias towards models with smaller parameter space,
but rather allows it to manifest in a very dangerous way.
The method strongly prefers the prior model with the narrowest distribution on
divergence times across all three of our analyses, even when this model is
almost certainly incorrect and excludes the true divergence times of the
Philippine taxa.
Unfortunately, ``checking'' the priors by plotting the summary statistics from
1000 random samples of each prior model along the first two orthogonal axes of
a principle component analysis, as recommended by \citet{Hickerson2013},
provides no warning of a problem (Figure~\ref{figPCA}.
Given that the results of \citet{Hickerson2013} strongly prefer the models with
the narrowest prior on divergence times, it seems quite likely that their
model-averaged results are dominated by models that exclude at least some of
the 22 true divergence times, making their results difficult to interpret
(in addition to the error of time units).

>>>>

        \vspace{12pt}
        Jamie R.\ Oaks$^{1,2}$, Jeet Sukumaran$^{3}$, Jacob A.\
        Esselstyn$^{4}$, Charles W.\ Linkem$^{5}$, Cameron D.\
        Siler$^{6}$, Mark T.\ Holder$^{1}$ and Rafe M.\ Brown$^{1}$

        \bigskip
        $^1$\emph{Department of Ecology and Evolutionary Biology,
            Biodiversity Institute,
            University of Kansas,
            Lawrence, Kansas 66045}\\[.1in]
        $^3$\emph{Department of Biology,
            Duke University,
            Durham, North Carolina 27708} \\[.1in]
        $^4$\emph{Museum of Natural Science,
            Louisiana State University,
            119 Foster Hall,
            Baton Rouge, Louisiana 70803}\\[.1in]
        $^5$\emph{Department of Biology,
            University of Washington,
            Seattle, Washington 98195}\\[.1in]
        $^6$\emph{Sam Noble Museum,
            Department of Biology,
            University of Oklahoma,
            Norman, Oklahoma 73072}\\[.1in]
        $^2$\emph{Corresponding author} (\href{mailto:joaks1@gmail.com}{\tt
        joaks1@gmail.com})\\

@@

{\sffamily
    \noindent\textbf{ABSTRACT} \\
    \noindent Recently, \citet{Oaks2012} presented a simulation-based
    assessment of the approximate Bayesian phylogeographical model choice
    method implemented in \msb, and found the method to lack robustness and
    power to detect temporal variation in divergences that are randomly
    distributed over relatively broad periods of evolutionary history.
    They conclude that a likely mechanism behind the bias toward models with
    few divergence events is the small marginal likelihoods of models with more
    divergence time parameters due to the integration over vast parameter space
    imposed by broad uniform priors characterized by low likelihood and high
    prior density.
    This phenomenon is often referred to as Lindley's paradox
    \citep{Lindley1957}.  \citet{Hickerson2013} have responded to this work,
    criticising the priors used by \citet{Oaks2012} and presenting an
    approximate Bayesian model-averaging approach that uses narrow, empirically
    informed uniform priors.
    \citet{Hickerson2013} conclude this approach circumvents the issues
    revealed by \citet{Oaks2012} and yields robust inference of divergence
    models.
    Furthermore, they argue that the biases revealed by \citet{Oaks2012} are
    inherent to the inefficient rejection algorithm implemented in \msb, rather
    than a result of Lindley's paradox.
    Here we show that their methodology suffered from a fundamental error that
    renders some of their results invalid and the remainder difficult to
    interpret.
    Furthermore, we demonstrate how their approach still suffers from a bias
    toward models with lesser parameter space, which manifests in a dangerously
    strong tendency to sample predominantly from models that exclude the true
    values of the model's parameters.
    Our results suggest that their model-averaged results are dominated by
    models that likely exclude at least some of the true divergence times
    across the 22 pairs of Philippine vertebrates, which adds to the
    difficulty in interpreting their results.
    We also show that in addition to this dangerous behavior, the approach of
    \citet{Hickerson2013} is still strongly biased toward inferring
    simultaneous divergences even when the true divergences are randomly
    distributed over millions of generations.
    Our results, coupled with those of \citet{Oaks2012}, strongly suggest that
    Lindley's paradox is a primary cause of the bias of \msb toward models with
    lesser parameter space.
    We discuss ways to mitigate this bias without resorting to adding an
    additional dimension of model choice to the model or using dangerous
    empirically informed uniform priors.

    \vspace{12pt}
    \noindent\textbf{KEY WORDS: Approximate Bayesian computation; Bayesian
        model choice; empirical Bayes}

}

\newpage
\noindent Recently, this journal has served as a medium for an interesting
discussion of the potential pitfalls of approximate Bayesian methods of
comparative phylogeographical model choice.
The discussion has centered around the approximate Bayesian model choice method,
\msb, which estimates the temporal distribution of divergences among
co-distributed pairs of taxa \citep{Huang2011} by sampling over all
unordered models of divergence.
\citet{Oaks2012} published results of simulation-based power analyses that
revealed that \msb can often be biased towards inferring models of temporally
clustered divergence times among taxon pairs.
\citet{Hickerson2013} has published a response to this paper where they present
an empirical Bayes model-averaging approach that they conclude circumvents the
poor behavior of the method revealed by \citet{Oaks2012}.
Both of these papers are largely in agreement.
In fact, \citet{Hickerson2013} reiterate a lot of the discussion of
\citet{Oaks2012} regarding the impact of broad uniform priors on Bayesian model
choice.
The main differences in their perspectives are centered around
(1) the mechanism by which broad uniform priors cause the poor behavior of
\msb, and
(2) how to potentially ameliorate this issue.

Regarding the mechanism behind the poor behavior of the method,
\citet{Oaks2012} suggest the primary cause is likely the low marginal
likelihoods of parameter-rich models integrated over vast parameter space with
low probability of producing the data, yet relatively high prior density
\citep[this is often referred to as Lindley's paradox;][]{Lindley1957}.
Note, this suggests the bias is extrinsic to \msb, and the numerical
approximation machinery of the method could be sound.
\citet{Hickerson2013} take a more pessimistic view of the bias, and suggest it
is intrinsic to \msb.
They conclude the method's rejection algorithm is inefficient and will be
increasingly biased as the overall space of the model increases, either as a
function of the number of taxon pairs or the width of the uniform priors on
nuisance parameters.
They support their position by giving a probabilistic argument that focuses on
only one of the three prior models used by \citet{Oaks2012}.
We show that this argument is based on an empirical Bayesian perspective
towards model choice and questionable assumptions, and does not explain the
bias of the method found in many of the analyses of \citet{Oaks2012}.
Furthermore, we reiterate several of the findings of \citet{Oaks2012} as well
as present results of additional analyses, which strongly suggest that
Lindley's paradox is playing a large role in the poor behavior of the method.

As for how to mitigate the bias, \citet{Oaks2012} suggest that more cogent
prior probability distributions on divergence models and nuisance parameters
could reduce the effect of Lindley's paradox.
They also layout a set of simulation-based procedures for determining power,
accuracy, and robustness of the method given a dataset, and recommend any
application of \msb should be accompanied by such procedures, especially if any
biological conclusions are drawn from the results.
\citet{Hickerson2013} present an approximate Bayesian model-averaging approach
for accommodating uncertainty in selecting among empirically guided priors, and
champion the method as a means of avoiding the pitfalls raised by
\citet{Oaks2012}.
Unfortunately, we show that fundamental errors in this approach render some of
their results invalid and leave the remaining results difficult to interpret.
Furthermore, we follow the advice of \citet{Oaks2012} and present
simulation-based assessments of Hickerson et al.'s (\citeyear{Hickerson2013})
approach.
Our results demonstrate that the method is biased and dangerous.  The approach
merely provides another means by which the model can ``escape'' large parameter
space, and bias toward smaller models remains.
This manifestation of the bias can be dangerous and often excludes the true
parameter space due to the use of narrow uniform priors.
Furthermore we discuss the potential theoretical and practical problems of
empirical Bayesian model choice, which is used and encouraged by
\citet{Hickerson2013} without any mention of its potential complications.

\section*{An error in Hickerson et al.'s re-analysis of the Philippines data}
\citet{Hickerson2013} re-analyzed the dataset of \citet{Oaks2012} using a
model-averaging approach, where they placed a discrete uniform prior over eight
different prior models (see Table 1 of \citet{Hickerson2013}).
In our initial attempts to explore the behavior of this approach, we found
a fundamental error in the methodology of \citet{Hickerson2013}:
their model mixes different time units.

Each of the eight prior models used in the re-analysis by \citet{Hickerson2013}
has one of two priors on the mean size of the descendant populations of each
taxon pair:
$\meanDescendantTheta{} \sim U(0.0001, 0.1)$ or
$\meanDescendantTheta{} \sim U(0.0005, 0.04)$.
As described in \citet{Oaks2012}, the divergence time parameters of the model
implemented in \msb are scaled relative to a constant reference population
size, \myTheta{C}.
This reference population size is defined in terms of the upper limit of the
uniform prior on the mean size of the descendant populations,
\meanDescendantTheta{}, such that for the prior $\meanDescendantTheta{} \sim
U(\uniformMin{\meanDescendantTheta{}},\uniformMax{\meanDescendantTheta{}})$,
$\myTheta{C} = \uniformMax{\meanDescendantTheta{}}/2$.
Thus, the model used by \citet{Hickerson2013} mixes two different units of
time.
In other words, some of their prior and posterior samples are in units of
$0.05/\mutationRate$ generations, whereas others are in units of
$0.02/\mutationRate$ generations.

The fact that their posterior samples are in different units makes the results
of \citet{Hickerson2013} difficult to interpret, and renders their
regression-adjusted results invalid; a fundamental assumption of regression is
that all of the values of the response variable are in the same units.
Thus, the results in sections ``Using ABC Model Comparison to Weight
Alternative Priors for the Philippine Vertebrate Data'' and ``Improved Sampling
Efficiency by Prior Weighting Supports Asynchronous and Recent Divergence for
the Philippines Vertebrate Data'' and presented in Figure 2 of
\citet{Hickerson2013} should be disregarded.
The error is easily illustrated by re-plotting their results with the different
time units indicated (Figure~\ref{figJointPosteriorHickerson}).
Another important characteristic of the approach used by \citet{Hickerson2013}
that makes their results difficult to interpret in addition to this error is
their use of narrow, empirically guided uniform priors in an approximate
Bayesian model choice framework.
We discuss the dangers of this approach in the next section, and show how the
results of \citet{Hickerson2013} likely exclude true values of the model's
parameters.

@@

\section*{The dangers of empirical Bayesian model choice}
\citet{Hickerson2013} repeatedly refer to the prior distributions used by
\citet{Oaks2012} as ``poorly selected''.
However, this is bit misleading, as \citet{Oaks2012} discuss in detail how they
selected their priors (see their section ``Specifying and simulating the joint
prior'').
They detail how being limited to uniform prior distributions in \msb
necessitates awkward broad priors to avoid excluding the truth, a priori.
What \citet{Hickerson2013} really mean by ``poorly selected'' is that
\citet{Oaks2012} did not use their data to inform their initial prior
distributions (i.e., they did not use an empirical Bayesian approach).
\citet{Oaks2012} did use empirically informed priors when assessing both the
prior sensitivity of the method and determining the power of \msb under
real-world conditions with highly informative priors.  \citet{Oaks2012} discuss
the potential dangers of taking an empirical Bayesian approach to model choice
(see the last paragraph of ``Assessing prior sensitivity of \msb'' in
\citet{Oaks2012}), and we expand on this here by exploring both the theoretical
and practical implications of using empirically informed priors for Bayesian
model choice.

@@

This is not to say that empirical Bayesian approaches are not useful.
Quite the contrary.
Empirical Bayes is a well studied branch of Bayesian statistics that
has given rise to a many powerful inference methods.
It is true that empirical Bayes methods have an uncertain theoretical basis and
do not yield a valid posterior distribution from Bayes' rule \citep[e.g.,
empirical Bayesian estimates of the posterior are often too narrow, off-center,
and misshapen;][]{Morris1983,Laird1987,Carlin1990,Efron2013}.
Nevertheless, empirical Bayes methods can provide a powerful means of parameter
estimation that often exhibit favorable frequentist properties.
Furthermore, many post-hoc correction methods have been developed for
estimating confidence-intervals from empirical Bayes estimates of posterior
distributions that often exhibit well-behaved frequentist coverage
probabilities
\citep{Morris1983,Laird1987,Laird1989, Carlin1990,Hwang2009}.

Whereas empirical Bayes approaches can provide powerful methods for parameter
estimation, a theoretical justification for empirical Bayes approaches to model
choice is much more questionable.
In Bayesian model choice, the goal is not to estimate parameters, but to
estimate the relative probabilities of candidate models.
Unlike parameter estimates, posterior probabilities represent a summary of the
entire posterior distribution.
Thus, given that empirical Bayesian posterior distributions are not accurate,
there is no guarantee regarding the accuracy of probabilities summarized from
them.

This can be demonstrated with a simple, albeit contrived, example.
Let us say that principal investigator Mary and her new postdoc Will are
interested in the hypothesis that the mass of George Washington's periwig
renders the quarter dollar of the United States unfair.
That is to say their null hypothesis is that the probability of a US
quarter landing heads when tossed is less than 0.5 ($\theta < 0.5$).
They can certainly evaluate this hypothesis, they can have undergraduate
worker, Joe, flip the coin for them while the tabulate the results.
But being Bayesians, before they call Joe into the lab, they agree on a
prior probability to place on the set of all possible probabilities that
the quarter will land heads when it is flipped.
Given that neither of them have a quarter, and their prior knowledge that Joe
moonlights as a magician, and is notorious for performing coin and card tricks
in the lab, they suspect there is a good chance that the quarter Joe uses will
be either two-headed or two-tailed.
So, knowing that the beta distribution is the conjugate prior for a binomial
likelihood, they decide to use a $beta(a=0.5, b=0.5)$ prior distribution
(Figure~\ref{figCoinFlip}).

Mary calls Joe into the lab, confirms that he has a quarter, and tells him to
begin flipping it.
After five tosses, four of which was heads, Joe decides that academics are
crazy and leaves the lab to pursue a major in theatre.  Mary and Will, both
being computational biologists, are satisfied with their
empirical dataset of $y = 4$ heads out of $N = 5$ trials.
They know from the conjugacy of the beta prior, that the posterior distribution
has the nice analytical form $\theta|y,N \sim beta(a + y, b + N - y)$, which
in this case is simply $beta(4.5, 1.5)$; this is the true posterior distribution
of $\theta$ given their prior belief and data (Figure~\ref{figCoinFlip}).
This allows them to plug these values into the beta cumulative distribution
function to determine that the posterior probability of their hypothesis is
$p(\theta < 0.5 | y=1, N=5) = 0.088$.
Given their prior belief and dataset, this indeed is the correct posterior
probability of the hypothesis, and Mary and Will should now update their
posterior belief accordingly.

However, reflecting upon the results of their experiment
(Figure~\ref{figCoinFlip}), Mary and Will regret their choice of prior.
Their prior looks very ``poorly selected,'' and if they had only known that the
coin was fair before the data were collected, they would have selected a much
better prior.
Clearly, from their results, they should have used a prior centered
around 0.2; their data suggest a prior of $beta(4.5, 1.5)$ would have been
much ``better.''
Rather than resort to flipping the coin five more times, Mary and Will decide
to redo their analysis using the much better ``prior'' of $p(\theta) \sim
beta(4.5, 1.5)$.
This gives a ``posterior'' of $\theta|y,N \sim beta(8.5, 2.5)$, and a
probability of their hypothesis of $p(\theta < 0.5 | y=1, N=5) = 0.026$.
Now convinced that the US quarter is unfair, albeit not due to the mass of
President Washington's head as they hypothesized, Will begins composing an
e-mail of complaint addressed to the U.S.\ Mint.

If Joe's flips were a representative sample, Mary and Will's empirical Bayes
estimate might very well be a better point estimate for the parameter
\myTheta{}.
However, their empirical Bayes estimate of the probability of their hypothesis
is incorrect and biased.
This simple example shows how parameter estimation is fundamentally different
from estimating the probability of a model.
While empirical informed priors can be used to obtain well-behaved parameter
estimators, using them for model choice is much less certain.
In addition to these theoretical concerns there are practical dangers to
using narrow, empirical, uniform priors for a method that has already
been shown to be biased toward models with lesser parameter space.

\subsection*{Practical dangers of narrow uniform priors for Bayesian model
choice}
We were alarmed when we saw the results of the model-averaging approach
used by \citet{Hickerson2013}.
Their results strongly favored the models with the narrowest, empirically
informed prior on divergence time, and thus their model-averaged posterior
estimates are dominated by models $M_1$ and $M_2$ (see Table 1 of
\citet{Hickerson2013}).
This concerned us because the narrowest \divt{} prior used by
\citet{Hickerson2013} ($\divt{} \sim U(0,0.1)$) likely excludes the true
divergence times for at least some of the Philippine taxa.
They set this prior to match the 95\% highest posterior density (HPD) interval for
the mean divergence time estimated under one of the priors used by
\citet{Oaks2012} (see Tables 2 and 3 of \citet{Oaks2012}).
Given this interval estimate is for the \emph{mean} divergence time across all
22 taxa, it seems odd to set this as the prior, because many of the taxon pairs
are expected to have diverged at times older than the upper limit.
Furthermore, this prior is \emph{excluded} from the 95\% HPD interval estimates
of the mean divergence time under the other two priors explored by
\citet{Oaks2012} (under these priors the 95\% HPD is approximately 0.3--0.6;
see Table~6 of \citet{Oaks2012}).
Thus, when we saw the results of \citet{Hickerson2013} we suspected that
Lindley's paradox was again biasing the method toward models with smaller
parameter space, and as a consequence was biasing the method toward models that
exclude the truth (i.e., toward estimating model-averaged posteriors
dominated by models that exclude true values of parameters of the model).

@@

For our re-analysis of the Philippines dataset we used the model-averaging
approach of \citet{Hickerson2013}, but with a reduced set of prior models to
avoid their error of mixing time units.
We used five prior models, all of which had priors on population sizes of
$\meanDescendantTheta{} \sim U(0.0001, 0.1)$ and $\ancestralTheta{} \sim
U(0.0001, 0.05)$.
Following \citet{Hickerson2013}, each of these models had the following
priors on divergence time parameters:
$M_1$, $\divt{} \sim U(0, 0.1)$;
$M_2$, $\divt{} \sim U(0, 1)$;
$M_3$, $\divt{} \sim U(0, 5)$;
$M_4$, $\divt{} \sim U(0, 10)$; and
$M_5$, $\divt{} \sim U(0, 20)$.
For our prior, we simulated $1\e6$ random samples from each of the models
for a total sample of $5\e6$.
For each model, we retained the 10,000 samples with the smallest Euclidean
distance from the observed summary statistics, standardizing the statistics
using the prior means and standard deviations of the given model.
From the remaining 50,000 samples, we then retained the 10,000 samples with the
smallest Euclidean distance from the observed summary statistics, this time
standardizing the statistics using the prior means and standard deviations
across all five models.
We then repeated this analysis twice, replacing the $M_1$ with
$M_{1A}$ and $M_{1B}$, which differ only by having priors on divergence
times of $\divt{} \sim U(0, 0.01)$ and $\divt{} \sim U(0, 0.001)$,
respectively.
While we suspect the prior of $\divt{} \sim U(0, 0.1)$ used by
\citet{Hickerson2013} likely excludes the true divergence times of at least
some of the 22 taxa, we are nearly certain that these narrower priors are
incorrect and exclude most, if not all, of the divergence times of the
Philippine taxa.

Our results show that the model-averaging approach of \citet{Hickerson2013}
does not reduce the method's bias toward models with lesser parameter space,
but rather allows it to manifest in a very dangerous way.
The method strongly prefers the prior model with the narrowest distribution on
divergence times across all three of our analyses, even when this model is
almost certainly incorrect and excludes the true divergence times of the
Philippine taxa (Table~\ref{tabModelChoiceEmpirical}).
Unfortunately, ``checking'' the priors by plotting the summary statistics from
1000 random samples of each prior model along the first two orthogonal axes of
a principle component analysis, as recommended by \citet{Hickerson2013},
provides no warning of a problem (Figure~\ref{figPCA}).
Given that the results of \citet{Hickerson2013} strongly prefer the models with
the narrowest prior on divergence times, it seems quite likely that their
model-averaged results are dominated by models that exclude at least some of
the 22 true divergence times, making their results difficult to interpret
(in addition to the error of time units).
